biological data preperation

### 2018-09-18 src/biological_data_prep.Rmd
trying to extract amo data to the species dataset...

>>>>

# Add AMO Data
The data has been prepared as per the environmental_data_preperation.Rmd

```{r}
amo <- read.csv("../output/env/amo.csv", header=TRUE)
head(amo)
```

So you want..
- AMO value at sampling month/year
- AMO value at previous sampling month/year
- AMO phase at previous winter (because the winter values are thought to be a major driver of ocean conditions in the following spring, summer, and autumn)

change month col names to numeric

```{r}
names(amo)[2:13] = c("1", "2","3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
head(amo)
```

to test this just subset some of your species data...
```{r}
test <- data_aea <- data_aea[data_aea$year < 2000,  ]
```

ok now do something...

subset cols 1:13
```{r}
testamo <- amo <- amo[ ,1:13]
testamo
```

```{r}
testamo <- reshape(testamo, 
  varying = c("1", "2","3", "4", "5", "6", "7", "8", "9", "10", "11", "12"),
  v.names = "value",
  direction = "long")

testamo.sort <- testamo[order(testamo$year),]
testamo
```

ok... soo now something like
where test$year = testamo$year AND test$month = testamo$time
  extract value
    add to new test$amo_sample
